### 2014-03-12 src/analysis.Rnw
update

df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction)
df$sqr <- 1 - df$r.square
df$mult <- 1 - df$score.multiplier
df$type <- with(df, as.factor(
      ifelse(grepl('line',operator), 'line',
        ifelse(grepl('block',operator), 'block',
        ifelse(grepl('method',operator), 'method',
          ifelse(grepl('class',operator), 'class',
            ifelse(grepl('project',operator), 'project',
              NA)))))))
df$strat <- with(df,
    ifelse(grepl('perunit', strategy), 'xpercent',
      ifelse(grepl('op',strategy), 'opsel',
        ifelse(grepl('one',strategy), 'oneperelm',
          ifelse(grepl('elem',strategy), 'loc', 'other'
            )))))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
\label{fig:fullimgsize}
\end{figure*}
\begin{figure*}[t]
<<op.all.2,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
\end{figure*}

>>>>

df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction) # & mutant.reduction < 20)
df$sqr <- 1 - df$r.square
df$mult <- 1 - df$score.multiplier
df$type <- with(df, as.factor(
      ifelse(grepl('line',operator), 'line',
        ifelse(grepl('block',operator), 'block',
        ifelse(grepl('method',operator), 'method',
          ifelse(grepl('class',operator), 'class',
            ifelse(grepl('project',operator), 'project',
              'selection')))))))
df$strat <- with(df,
    ifelse(grepl('perunit', strategy), 'xpercent',
      ifelse(grepl('op',strategy), 'opsel',
        ifelse(grepl('one',strategy), 'oneperelm',
          ifelse(grepl('elem',strategy), 'loc', 'other'
            )))))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
\label{fig:fullimgsize}
\end{figure*}
\begin{figure*}[t]
<<op.all.2,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
\end{figure*}
